### 2014-08-02 paper/paper.tex
On my way to a program with cross validation
Changed the formatting of the doc but I am yet to number the sections
Numbered sections. Hopefully fixed the crossfolds in the makefile
Added a license. Stubbed the changed Fei Song recomended. Fixed the data for the boxplot

\documentclass[12pt]{article}
\usepackage{enumerate}
\usepackage{courier}
\usepackage{graphicx}
\usepackage[margin=1.0in]{geometry}
\usepackage{float}
\usepackage{setspace}
\usepackage[numbers]{natbib}

@@

\makeatletter
\renewcommand\@seccntformat[1]{}
\makeatother

@@

\subsection{Topic Area}

@@

@@

%TODO extend

\section{Approach}

@@

\subsection{Implementation}

@@

@@

\subsection{Avoiding overfitting}

@@

\section{Discussion}

\subsection{Evaluation Method}

After the SemEval-2013 workshop the organizers released a paper discussing the
proceedings and the results of the task \cite{Nakov2013}. The paper establishes
baseline in terms of $F$. $F$ can be calculated $F = (F_{pos} + F_{neg}) / 2$
where $F_{pos} = 2 \frac{P_{pos}R_{pos}}{P_{pos} + R_{pos}}$ and $F_{neg}$ is
calculated in a similar fashion. The \textit{Precision} measure for the
positive label is $P_{pos} = \frac{\mathrm{\# of\ true\ postive}}{\mathrm{\#
of\ true\ postive} + \mathrm{\# of\ false\ postive} }$. The \textit{Recall}
measure for the positive label is defined as $R_{pos} = \frac{\mathrm{\# of\
true\ postive}}{\mathrm{\# of\ true\ postive} + \mathrm{\# of\ false\ negative}
}$

@@

The proceedings of SemEval-2013 establishes the `Majority Baseline' for the
task to be an F-score of 29.19. How this number is calculated is not discusses
in paper.

@@

\subsection{Results}

@@

@@

@@

\subsection{Comparison to Workshop Participants}

@@

\section{Conclusion}

@@

\section{Future Work}

\subsection{Hashtags}

@@

\subsection{Users}

@@

% Bibliography
\nocite{*}
\bibliographystyle{ieeetr}
\bibliography{paper}

>>>>

%\documentclass[12pt]{article}
\documentclass[final,3p,12pt]{elsarticle}
\usepackage{enumerate}
\usepackage{courier}
\usepackage{graphicx}
%\usepackage[margin=1.0in]{geometry}
\usepackage{float}
\usepackage{setspace}
\usepackage[numbers]{natbib}

@@

@@

@@

%TODO Sentiment Analysis
%TODO Text Classification
%TODO Feature Selection

@@

\section{Our Implementation}

@@

% TODO expand on IIS

\subsection{Preprocessing and Feature Selection}

@@

    %TODO talk about cross validation

@@

\subsection{Training Optimization}

@@

\section{Experiments and Discussion}

\subsection{Dataset}

\subsection{Evaluation Measures}

After the SemEval-2013 workshop the organizers released a paper discussing the
proceedings and the results of the task \cite{Nakov2013}. The paper establishes
baseline in terms of $F$. $F$ can be calculated as:
\begin{equation}
    F = \frac{2 \frac{P_{pos}R_{pos}}{P_{pos} + R_{pos}} +
    2 \frac{P_{neg}R_{neg}}{P_{neg} + R_{neg}}}{2}
\end{equation}

Which can be simplified to:

\begin{equation}
    F = \frac{P_{pos}R_{pos}}{P_{pos} + R_{pos}} + \frac{P_{neg}R_{neg}}{P_{neg} + R_{neg}}
\end{equation}

The \textit{Precision} measure for the positive label is $P_{pos} =
\frac{\mathrm{\# of\ true\ postive}}{\mathrm{\# of\ true\ postive} + \mathrm{\#
of\ false\ postive} }$. The \textit{Recall} measure for the positive label is
defined as $R_{pos} = \frac{\mathrm{\# of\ true\ postive}}{\mathrm{\# of\ true\
postive} + \mathrm{\# of\ false\ negative} }$. $P_{neg}$ and $R_{neg}$ can be
calculated in a similar fashion.

@@

@@

\subsection{Experimental Results}

@@

% TODO Student T-test

@@

%TODO talk about the features

@@

\subsection{Comparison to Other Systems}

@@

\section{Conclusions and Future Work}

\subsection{Conclusions}

@@

\subsection{Future Work}

\subsubsection{Hashtags}

@@

\subsubsection{Users}

@@

\section{References}

\nocite{*}
\bibliographystyle{ieeetr}
\bibliography{paper}

\section{Appendices}

\subsection{Implementation Source Code}
